\texttt{MSnbase}, efficient R-based access and manipulation of raw mass spectrometry data

### 2020-04-27 msnbase2.Rnw
vis fig (from centroiding vignette)

<<bc1, echo=TRUE, eval=FALSE>>=
raw_bc %>% 
    bc_groups() %>%       ## identify BoxCar groups (bc_groups)
    filterBoxCar() %>%    ## keep only BoxCar spectra
    bc_zero_out_box() %>% ## remove signal outside of BoxCar segments
    combineSpectra(fcol = "bc_groups", ## reconstruct full spectrum
                   method = boxcarCompbine)
@

@@

The R environment is well known for the quality of its visualiation
capacity. This also holds true for mass
spectrometry\cite{Gatto:2015,protViz}.

@@

\item{potential for reuse}: see
  \cite{Wieczorek:2017,Griss:2019,Smith:2006} for examples.
\item{general limitations}
\item{system limitations}
\item{end-user documentation}
\item{developer documentation}
\item{sample data}
\item{benchmark data set}
\item{availability}
\item{license information}
\item{system requirements}

>>>>

<<bc1, echo=TRUE, eval=FALSE>>=
bc <- readMSData("boxcar.mzML", mode = "onDisk") %>%
      bc_groups() %>%       ## identify BoxCar groups (bc_groups)
      filterBoxCar() %>%    ## keep only BoxCar spectra
      bc_zero_out_box() %>% ## remove signal outside of BoxCar segments
      combineSpectra(fcol = "bc_groups", ## reconstruct full spectrum
                     method = boxcarCompbine)
@

@@

The R environment is well known for the quality of its visualiation
capacity. This also holds true for mass
spectrometry\cite{Gatto:2015,protViz,Pviz,Bemis:2015}. Here, we
conclude the overview of version 2 of the \texttt{MSnbase} package by
highlighting the flexibility of the software to visualise and assess
the efficiency of raw data processing.

@@

\item{potential for reuse}: see
  \cite{Smith:2006,Wieczorek:2017,Griss:2019} for examples.
\item{general limitations}
\item{system limitations}
\item{end-user documentation}
\item{developer documentation}
\item{sample data}
\item{benchmark data set}
\item{availability}
\item{license information}
\item{system requirements}
